Expert-In-The-Loop Causal Discovery: Iterative Model Refinement Using Expert Knowledge

### 2025-02-04 paper/main.tex
Updates

@@

\section{Background and Related Work}
\label{sec:background}
\subsection{Notations}
We denote random variables with uppercase letters $ X $, and a set of random
variables as $ \bm{X} = \{X_1, \cdots, X_k\} $ with $ \rvert \bm{X} \rvert = k
$. A sample from the random variable $ X $ is denoted as $ x $ and from a set
of random variables $ \bm{X} $ is denoted as $ \bm{x} $. In this paper, we
consider random variables in the mixed data setting where each of the random
variables can be continuous, categorical, or ordinal unless specified.

@@

\subsection{Measures of Conditional Association}
Our proposed method for iterative DAG construction relies on a measure of
conditional association between variables. We are interested in measuring the
association between variables $ X $ and $ Y $ when conditioned on a set of
variables $ \bm{Z} $ which is potentially an empty set, $ \bm{Z} = \emptyset $.
Depending on the type of $ X $, $ Y $, and $ \bm{Z} $ various measures of
associations have been used. Typically, these are the effect size measures of
the conditional independence test $ X \ci Y \rvert \bm{Z} $. Here, we give an
overview of some of the commonly used measures for different data types.

>>>>

\todo[inline]{The following three paragraphs need work.}

@@

\section{Background and Related Work}
\label{sec:background}
\subsection{Notations}
We denote random variables with uppercase letters $ X $, and a set of random
variables as $ \bm{X} = \{X_1, \cdots, X_k\} $ with $ \rvert \bm{X} \rvert = k
$. A sample from the random variable $ X $ is denoted as $ x $ and from a set
of random variables $ \bm{X} $ is denoted as $ \bm{x} $. In this paper, we
consider random variables in the mixed data setting where each of the random
variables can be either of continuous, categorical, or ordinal unless
specified.

@@

\subsection{Measures of Conditional Association}
Our proposed method for iterative DAG construction relies on a measure of
conditional association also known as partial association between variables. We
are interested in measuring the association between variables $ X $ and $ Y $
when conditioned on a set of variables $ \bm{Z} $ which is potentially an empty
set, $ \bm{Z} = \emptyset $. Many special case measures of conditional
association have been used in literature depending on the type of $ X $, $ Y $,
and $ \bm{Z} $. Typically, these are the effect size measures of the
conditional independence test $ X \ci Y \rvert \bm{Z} $. In this section, we
give an overview of some of the commonly used measures for different data
types.
